Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-10-08 manuscript.Rmd

After researchers are satisfied with their draft preregistration, they should create an archived and unchangeable version of the project that serves as the preregistration.
zenodo.org [@zenodo] is a publicly funded service provider that archives digital artefacts for research and provides digital object identifiers (DOI) for these archives.
While the service is independent of GitHub---in terms of storage facilities and financing---you can link GitHub and zenodo.org.
Please note that you can only link public GitHub repositories to zenodo.org.
You may log into zenodo.org through your GitHub account.

> Log into zenodo.org → Account → GitHub[^zenodo-github]
[^zenodo-github]: https://zenodo.org/account/settings/github/

@@

```{r}
usethis::browse_github()
```

>>>>

After researchers are satisfied with their draft preregistration, they should create an archived and unchangeable version of the project that serves as the preregistration.
zenodo.org [@zenodo] is a publicly funded service provider that archives digital artefacts for research and provides digital object identifiers (DOI) for these archives.
While the service is independent of GitHub---in terms of storage facilities and financing---you can link GitHub and zenodo.org.
Please note that you can only link public GitHub repositories to zenodo.org.
You may log into zenodo.org through your GitHub account.
To log in with your GitHub account:

> Navigate to https://zenodo.org/login/ →  Log in with GitHub

\noindent{}To link zenodo.org and GitHub

> Log into zenodo.org → Account → GitHub[^zenodo-github]

\noindent{}Or:

> Navigate to https://zenodo.org/account/settings/github/

[^zenodo-github]: https://zenodo.org/account/settings/github/

@@

```{r, eval=FALSE}
usethis::browse_github()
```
